Draft Final Report: Measles risk assessment, modelling, and benefit--cost analyses for New Zealand

### 2015-06-12 draftfinalreport_v4.Rnw
remove the light grey sea comments :(
unamericanise the dates

\begin{sidewaysfigure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{2013totnp2.pdf}
\end{center}
\caption{Measles incidence per million, 2013. Dark grey indicates no data were available. Light grey is sea. Data: WHO (\href{http://www.who.int/research/en/}{www.who.int/research/en/}). Grey indicates not reported.}
\label{fig:incidence12}
\end{sidewaysfigure}

\begin{sidewaysfigure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{2013totnp3.pdf}
\end{center}
\caption{Measles vaccination cover (\% coverage of children that receive one dose of measles vaccine by their second birthday.), 2013. Dark grey indicates no data were available. Light grey is sea. Data: WHO (\href{http://www.who.int/research/en/}{www.who.int/research/en/}). Grey indicates not reported.}
\label{fig:cover12}
\end{sidewaysfigure}

\begin{sidewaysfigure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{2013np1.pdf}
\end{center}
\caption{Non-New Zealander international travel and immigration by 0--19 year olds, 2013. Dark grey indicates no data were available. Light grey is sea.)}
\label{fig:immigration12}
\end{sidewaysfigure}

\begin{sidewaysfigure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{2013nznp1.pdf}
\end{center}
\caption{New Zealander international travel, 2013. Dark grey indicates no data were available. Light grey is sea.}
\label{fig:nztravel12}
\end{sidewaysfigure}

\begin{sidewaysfigure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{2013totnp1.pdf}
\end{center}
\caption{Total international travel by 0--19 year old non New Zealanders and all ages of New Zealanders, 2013. Dark grey indicates no data were available. Light grey is sea.}
\label{fig:travel12}
\end{sidewaysfigure}

\begin{sidewaysfigure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{2013totnp4.pdf}
\end{center}
\caption{Risk map for measles importation, based on measles incidence and non-New Zealander 0--19 year old and all ages of New Zealander travel figures, 2013. Dark grey indicates no data were available. Light grey is sea.}
\label{fig:risk12}
\end{sidewaysfigure}

\begin{sidewaysfigure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{2013nznp4.pdf}
\end{center}
\caption{Risk map for measles importation from New Zealander international travel, based on measles incidence and travel figures, 2013. Dark grey indicates no data were available. Light grey is sea.}
\label{fig:nzrisk12}
\end{sidewaysfigure}

\begin{sidewaysfigure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{2013np4.pdf}
\end{center}
\caption{Risk map for measles importation from 0--19 year old non-New Zealander international travel and immigration and measles incidence, 2013. Dark grey indicates no data were available. Light grey is sea.}
\label{fig:imrisk12}
\end{sidewaysfigure}

@@

Direct costs for measles management in New Zealand for the 10-week period, January 1 -- March 9, 2014 are shown in  \autoref{table:direct}. The reported direct medical costs do not include hospital medical costs, which are reported separately in \autoref{table:hosp}.

\begin{table}
<<results=tex,echo=FALSE>>=
latex(costtable1, file="", table.env=FALSE,rowname=NULL)
@
\caption{Estimated costs (NZ\$) for measles public health management in New Zealand, January 1 -- March 9, 2014. PHN: public health nurse; PHA: public health assistant; IMT: incident management team; SSO: safety/security officer (SSO)}
\label{table:direct}
\end{table}

@@

\begin{table}
<<results=tex,echo=FALSE>>=
colnames(costtable2) <- c("Year", "Cases", "Days", "Cost","Cost per case","Cost per day")
latex(costtable2, file="", table.env=FALSE,rowname=NULL)
@
\caption{Reported direct hospitalisation costs in NZ\$, with the number of cases (Cases), length of hospital stay (Days), total cost (Cost, NZ\$), cost per case (NZ\$) and cost per day (NZ\$) for patients with measles as the primary diagnosis, 2000--2014}
\label{table:hosp}
 \centering
 \begin{tablenotes}
      \small
      \item As of 11 July, 2014. NC - not calculated.
    \end{tablenotes}
\end{table}

From 16 December, 2013 through 19 June, 2014 there were 201 confirmed measles cases in New Zealand (note 14 of these occurred before 1 January 2014, so 187 occurred from January 2014 -- 19 June 2014). The number of cases by age group is shown in \autoref{table:freq}. Of these 201 cases, 34 (17\%) were admitted to hospital with the highest proportion occurring in the youngest (< 15 months) and oldest (> 19 years) age groups, 47\% and 33\%, respectively.

\begin{table}
<<results=tex,echo=FALSE>>=
latex(costtable3, file="", table.env=FALSE,rowname=NULL)
@
\caption{Frequency of measles cases and number and proportion admitted to hospital by age group, 16 December, 2013 -- 19 June, 2014. Data from ESR.}
\label{table:freq}
\end{table}

>>>>

\begin{sidewaysfigure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{2013totnp2.pdf}
\end{center}
\caption{Measles incidence per million, 2013. Dark grey indicates no data were available. Data: WHO (\href{http://www.who.int/research/en/}{www.who.int/research/en/}). Grey indicates not reported.}
\label{fig:incidence12}
\end{sidewaysfigure}

\begin{sidewaysfigure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{2013totnp3.pdf}
\end{center}
\caption{Measles vaccination cover (\% coverage of children that receive one dose of measles vaccine by their second birthday.), 2013. Dark grey indicates no data were available. Data: WHO (\href{http://www.who.int/research/en/}{www.who.int/research/en/}). Grey indicates not reported.}
\label{fig:cover12}
\end{sidewaysfigure}

\begin{sidewaysfigure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{2013np1.pdf}
\end{center}
\caption{Non-New Zealander international travel and immigration by 0--19 year olds, 2013. Dark grey indicates no data were available.}
\label{fig:immigration12}
\end{sidewaysfigure}

\begin{sidewaysfigure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{2013nznp1.pdf}
\end{center}
\caption{New Zealander international travel, 2013. Dark grey indicates no data were available.}
\label{fig:nztravel12}
\end{sidewaysfigure}

\begin{sidewaysfigure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{2013totnp1.pdf}
\end{center}
\caption{Total international travel by 0--19 year old non New Zealanders and all ages of New Zealanders, 2013. Dark grey indicates no data were available.}
\label{fig:travel12}
\end{sidewaysfigure}

\begin{sidewaysfigure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{2013totnp4.pdf}
\end{center}
\caption{Risk map for measles importation, based on measles incidence and non-New Zealander 0--19 year old and all ages of New Zealander travel figures, 2013. Dark grey indicates no data were available.}
\label{fig:risk12}
\end{sidewaysfigure}

\begin{sidewaysfigure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{2013nznp4.pdf}
\end{center}
\caption{Risk map for measles importation from New Zealander international travel, based on measles incidence and travel figures, 2013. Dark grey indicates no data were available.}
\label{fig:nzrisk12}
\end{sidewaysfigure}

\begin{sidewaysfigure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{2013np4.pdf}
\end{center}
\caption{Risk map for measles importation from 0--19 year old non-New Zealander international travel and immigration and measles incidence, 2013. Dark grey indicates no data were available.}
\label{fig:imrisk12}
\end{sidewaysfigure}

@@

Direct costs for measles management in New Zealand for the 10-week period, 1 January -- 9 March 2014 are shown in  \autoref{table:direct}. The reported direct medical costs do not include hospital medical costs, which are reported separately in \autoref{table:hosp}.

\begin{table}
<<results=tex,echo=FALSE>>=
latex(costtable1, file="", table.env=FALSE,rowname=NULL)
@
\caption{Estimated costs (NZ\$) for measles public health management in New Zealand, 1 January -- 9 March 2014. PHN: public health nurse; PHA: public health assistant; IMT: incident management team; SSO: safety/security officer (SSO)}
\label{table:direct}
\end{table}

@@

\begin{table}
<<results=tex,echo=FALSE>>=
colnames(costtable2) <- c("Year", "Cases", "Days", "Cost","Cost per case","Cost per day")
latex(costtable2, file="", table.env=FALSE,rowname=NULL)
@
\caption{Reported direct hospitalisation costs in NZ\$, with the number of cases (Cases), length of hospital stay (Days), total cost (Cost, NZ\$), cost per case (NZ\$) and cost per day (NZ\$) for patients with measles as the primary diagnosis, 2000--2014}
\label{table:hosp}
 \centering
 \begin{tablenotes}
      \small
      \item As of 11 July 2014. NC - not calculated.
    \end{tablenotes}
\end{table}

From 16 December 2013 through 19 June 2014 there were 201 confirmed measles cases in New Zealand (note 14 of these occurred before 1 January 2014, so 187 occurred from January 2014 -- 19 June 2014). The number of cases by age group is shown in \autoref{table:freq}. Of these 201 cases, 34 (17\%) were admitted to hospital with the highest proportion occurring in the youngest (< 15 months) and oldest (> 19 years) age groups, 47\% and 33\%, respectively.

\begin{table}
<<results=tex,echo=FALSE>>=
latex(costtable3, file="", table.env=FALSE,rowname=NULL)
@
\caption{Frequency of measles cases and number and proportion admitted to hospital by age group, 16 December 2013 -- 19 June 2014. Data from ESR.}
\label{table:freq}
\end{table}
